\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2015-07-13 doc/USER_MANUAL/authors.tex
merged the SPECFEM3D and SPECFEM3D_GLOBE list of authors (too difficult to distinguish them, and does not make much sense)

\noindent The SPECFEM3D Cartesian package was first developed by Dimitri
Komatitsch and Jean-Pierre Vilotte at Institut de Physique du Globe
(IPGP) in Paris, France from 1995 to 1997 and then by Dimitri Komatitsch
and Jeroen Tromp at Harvard University and Caltech, USA, starting in 1998.
The story started on April 4, 1995, when Prof. Yvon Maday from CNRS and University of Paris, France, gave a lecture to
Dimitri Komatitsch and Jean-Pierre Vilotte at IPG about the nice properties of the Legendre spectral-element method with diagonal mass matrix that he had used for
other equations. We are deeply indebted and thankful to him for that.
That followed a visit by Dimitri Komatitsch to OGS (Istituto Nazionale di Oceanografia e di Geofisica Sperimentale) in Trieste, Italy, in February 1995
to meet with G\'eza Seriani and Enrico Priolo, who introduced him to their 2D Chebyshev version of the spectral-element method with a non-diagonal mass matrix.
We are deeply indebted and thankful to them for that.

%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
Since then it has been developed and maintained by a development team:
in alphabetical order,
Jean-Paul (Pablo) Ampuero,
Kangchen Bai,
Piero Basini,
C\'eline Blitz,
Alexis Bottero,
Ebru Bozda\u{g},
Emanuele Casarotti,
Joseph Charles,
Min Chen,
Paul Cristini,
Percy Galvez,
Dominik G\"oddeke,
Vala Hj\"orleifsd\'ottir,
Sue Kientz,
Dimitri Komatitsch,
Jes\'us Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Matthieu Lefebvre,
Qinya Liu,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
Ren\'e Matzen,
Dennis McRitchie,
Matthias Meschede,
Peter Messmer,
David Mich\'ea,
Surendra Nadh Somala,
Tarje Nissen-Meyer,
Daniel Peter,
Max Rietmann,
Elliott Sales de Andrade,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Jean-Pierre Vilotte,
Zhinan Xie,
Chang-Hua Zhang,
Hejun Zhu.\\

The cover graphic of the manual was created by Santiago Lombeyda from
Caltech's Center for Advanced Computing Research (CACR) \urlwithparentheses{http://www.cacr.caltech.edu}.\\

>>>>

\noindent The SPECFEM3D package was first developed by Dimitri
Komatitsch and Jean-Pierre Vilotte at Institut de Physique du Globe
(IPGP) in Paris, France from 1995 to 1997 and then by Dimitri Komatitsch
and Jeroen Tromp at Harvard University and Caltech, USA, starting in 1998.
The story started on April 4, 1995, when Prof. Yvon Maday from CNRS and University of Paris, France, gave a lecture to
Dimitri Komatitsch and Jean-Pierre Vilotte at IPG about the nice properties of the Legendre spectral-element method with diagonal mass matrix that he had used for
other equations. We are deeply indebted and thankful to him for that.
That followed a visit by Dimitri Komatitsch to OGS (Istituto Nazionale di Oceanografia e di Geofisica Sperimentale) in Trieste, Italy, in February 1995
to meet with G\'eza Seriani and Enrico Priolo, who introduced him to their 2D Chebyshev version of the spectral-element method with a non-diagonal mass matrix.
We are deeply indebted and thankful to them for that.

%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
Since then it has been developed and maintained by a development team: in alphabetical order,
Michael Afanasiev,
Jean-Paul (Pablo) Ampuero,
Kangchen Bai,
Piero Basini,
C\'eline Blitz,
Alexis Bottero,
Ebru Bozda\u{g},
Emanuele Casarotti,
Joseph Charles,
Min Chen,
Paul Cristini,
Cl\'ement Durochat,
Percy Galvez,
Dominik G\"oddeke,
Vala Hj\"orleifsd\'ottir,
Sue Kientz,
Dimitri Komatitsch,
Jes\'us Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Matthieu Lefebvre,
Qinya Liu,
David Luet,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
Ren\'e Matzen,
Dennis McRitchie,
Matthias Meschede,
Peter Messmer,
David Mich\'ea,
Vadim Monteiller,
Surendra Nadh Somala,
Tarje Nissen-Meyer,
Daniel Peter,
Kevin Pouget,
Max Rietmann,
Elliott Sales de Andrade,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
James Smith,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Brice Videau,
Jean-Pierre Vilotte,
Zhinan Xie,
Chang-Hua Zhang,
Hejun Zhu.\\

The cover graphic of the manual was created by Santiago Lombeyda from
Caltech's Center for Advanced Computing Research (CACR), USA, with free satellite clipart pictures
from \url{http://www.4vector.com} and \url{http://www.clker.com} added to it.\\
